---
title: "Automate Plotting"
subtitle: ""
author: "Jae Yeon Kim"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

# Setup 

```{r}
# Install packages 
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, # tidyverse pkgs including purrr
               tictoc, # performance test 
               glue) # glue strings and objects 
```

# Objective 

- Learning how to use `map()` and `glue()` to automate creating multiple plots

# Problem 

- Making the following data visualization process more efficient. 

```{r}
data("airquality")

airquality
```


```{r}
airquality %>%
    ggplot(aes(x = Ozone, y = Solar.R)) +
    geom_point() +
    labs(title = "Relationship between Ozone and Solar.R",
         y = "Solar.R")

airquality %>%
    ggplot(aes(x = Ozone, y = Wind)) +
    geom_point() +
    labs(title = "Relationship between Ozone and Wind",
         y = "Wind")

airquality %>%
    ggplot(aes(x = Ozone, y = Temp)) +
    geom_point() +
    labs(title = "Relationship between Ozone and Temp",
         y = "Temp")
```

# Solution 

- Learn how `glue()` works. 
- `glue()` combines strings and objects and it works simpler and faster than `paste()` or `sprintif()`.

```{r}

names <- c("Jae", "Aniket", "Avery")

fields <- c("Political Science", "Law", "Public Health")

library(glue)
glue("{names} studies {fields}.")

```

- So, our next step is to combine `glue()` and `map()`. 

- Let's first think about writing a function that includes `glue()`.

**Challenge 1**
How can you create the character vector of column names? 

**Challenge 2**
How can make `ggplot2()` take strings as x and y variable names?

```{r, warning = F, message = F}

airquality %>%
      ggplot(aes(x = .data[[names(airquality)[1]]], y = .data[[names(airquality)[2]]]))+
    geom_point()+
    labs(title = glue("Relationship between Ozone and {names(airquality)[2]}"),
         y = glue("{names(airquality)[2]}"))

```

- The next step is to write an automatic plotting function. 

    - Note that in the function i (abstract argument) replaced 2 (specific number). 

```{r}

create_point_plot <- function(i){
  
  p <- airquality %>%
    ggplot(aes(x = .data[[names(airquality)[1]]], y = .data[[names(airquality)[i]]]))+
    geom_point() +
    labs(title = glue("Relationship between Ozone and {names(airquality)[i]}"),
         y = glue("{names(airquality)[i]}"))
  print(p)
}

```

- The final step is to put the function in `walk()`.

```{r, message = F, warning = F}

walk(2:ncol(airquality), create_point_plot)

```
