---
title: "Automate Simulations"
subtitle: ""
author: "Jae Yeon Kim"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

# Setup 

```{r}
# Install packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse, # tidyverse pkgs including purrr
  tictoc, # performance test
  gapminder # toy data 
) 
```

# Objective 

- Learning how to use `rerun()` to automate running multiple simulations

Simulations are a great way [to check statistical assumptions and learn how statistical models work](http://people.duke.edu/~ccc14/sta-663-2016/15B_ResamplingAndSimulation.html). 

# Problem 

- Can you run the following regression model 1,000 times and plot the predicted values ($\hat{y}$) and their confidence intervals? 

```{r}

data("gapminder")

# Build a regression model
model <- lm(lifeExp ~ log(gdpPercap), data = gapminder)

# Predict y-values
gapminder$pred <- predict(model, type = "response", gapminder)

# Predict confidence intervals
ilink <- family(model)$linkinv # Extracting the inverse link from parameter objects

# Combine prediction outputs
combined <- predict(model, gapminder, se.fit = TRUE)[1:2] %>% as_tibble() %>%
    mutate(
      upr = ilink(fit + (2 * se.fit)),
      lwr = ilink(fit - (2 * se.fit))
    ) %>%
    bind_cols(gapminder)

combined %>%
  ggplot(aes(x = log(gdpPercap), y = lifeExp)) +
  geom_point(alpha = 0.2) +
  geom_line(aes(y = pred), size = 1, col = "blue") +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.4) +
  scale_y_continuous(breaks = scales::pretty_breaks())

```

# Solution 

## Write a function 

```{r}

predict_lm <- function(input) {

  # Build a regression model
  model <- lm(lifeExp ~ log(gdpPercap), data = input)

  # Predict y-values
  input$pred <- predict(model, type = "response", input)

  # Predict confidence intervals
  ilink <- family(model)$linkinv # Extracting the inverse link from parameter objects

  # Combine prediction outputs
  output <- predict(model, input, se.fit = TRUE)[1:2] %>%
    as_tibble() %>%
    mutate(
      upr = ilink(fit + (2 * se.fit)),
      lwr = ilink(fit - (2 * se.fit))
    ) %>%
    bind_cols(input)

  output 
}

# Unit testing  
testthat::expect_equal(sum(colnames(predict_lm(gapminder)) %in% c("fit", "se.fit")), 2)

```

## for loop 

```{r}

fit <- rep(NA, nrow(gapminder))
se.fit <- rep(NA, nrow(gapminder))

for (i in 1:1000){
  
    # Build a regression model
  model <- lm(lifeExp ~ log(gdpPercap), data = gapminder)

  # Predict y-values and SEs 
  fit[i] <- predict(model, gapminder, se.fit = TRUE)[1]
  se.fit[i] <- predict(model, gapminder, se.fit = TRUE)[2] 
  
}

fit
```

## rerun

### Write a function 

```{r}

predict_lm <- function(input) {

  # Build a regression model
  model <- lm(lifeExp ~ log(gdpPercap), data = input)

  # Predict y-values
  input$pred <- predict(model, type = "response", input)

  # Predict confidence intervals
  ilink <- family(model)$linkinv # Extracting the inverse link from parameter objects

  # Combine prediction outputs
  output <- predict(model, input, se.fit = TRUE)[1:2] %>%
    as_tibble() %>%
    mutate(
      upr = ilink(fit + (2 * se.fit)),
      lwr = ilink(fit - (2 * se.fit))
    ) %>%
    bind_cols(input)

  output 
}

```
