---
title: "Make Automation Slower or Faster"
subtitle: ""
author: "Jae Yeon Kim"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

# Setup 

```{r}
# Install packages 
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, # tidyverse pkgs including purrr
               tictoc, # performance test 
               furrr) # parallel processing 
```

# Objectives 

- Learning how to use `slowly()` and `future_` to make automation process either slower or faster

# How to Make Automation Slower

- Scraping 50 pages from a website and you don't want to overload the server. How can you do that?

# For loop 

```{r, include=FALSE}

for(i in 1:50){
  
  message("Scraping page ",i)
  
  if((i %% 10) == 0){
    
    message("Break time")
    
    Sys.sleep(1) # 1 second 
  }
  
}

```
# Map 

- `walk()` works same as `map()` but doesn't store its output. 

```{r,include=FALSE}

walk(1:50, function(x){message("Scraping page", x)})

```
- If you're web scraping, one problem with this approach is it's too fast by human standards.

```{r,include=FALSE}

# 0.03 sec elapsed 
tic()
walk(1:50, function(x){message("Scraping page", x)}) # Anonymous function; I don't name the function 
toc()

```
- If you want to make the function run slowly ... 

> slowly() takes a function and modifies it to wait a given amount of time between each call. - `purrr` package vignette 

- If a function is a verb, then a helper function is an adverb (modifying the behavior of the verb). 

```{r,include=FALSE}

# 49.05 sec elapsed


tic()

walk(1:50, slowly(function(x){message("Scraping page", x)},   
                    rate = rate_delay(pause = 1))) # pause = Delay between attempts in seconds

toc()

```
# How to Make Automation Faster 

In a different situation, you want to make your function run faster. This is a common situation when you collect and analyze data at large-scale. You can solve this problem using parallel processing. For more on the parallel processing in R, read [this review](https://yxue-me.com/post/2019-05-12-a-glossary-of-parallel-computing-packages-in-r-2019/).

- Parallel processing setup 

    - Step1: Determine the number of max workers (`availableCores()`)
    
    - Step2: Determine the parallel processing mode (`plan()`) 

```{r}

# Setup 
n_cores <- availableCores() - 1
n_cores # This number depends on your computer spec.

plan(multiprocess, # multicore, if supported, otherwise multisession
     workers = n_cores) # the maximum number of workers

# 4.931 sec elapsed 
tic()
mean100 <- map(1:1000000, mean)
toc()

# 2.536 sec elapsed 
tic()
mean100 <- future_map(1:1000000, mean)
toc()

```

