---
title: "Make Error Handling Easier"
subtitle: ""
author: "D-Lab"
output:
  html_document:
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

# Setup 

```{r}
# Install packages 
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, # tidyverse pkgs including purrr
               rvest) # web scraping 
```

# Learning objective 

- Learning how to use `safely()` and `possibly()` to make error handling easier 

# Problem 

**Challenge 1**

- Explain why we can't run `map(url_lists, read_html)`



```{r}

url_lists <- c("https://en.wikipedia.org/wiki/University_of_California,_Berkeley",
"https://en.wikipedia.org/wiki/Stanford_University",
"https://en.wikipedia.org/wiki/Carnegie_Mellon_University",
"https://DLAB" 
)

```

```{r, eval=FALSE}

map(url_lists, read_html)

```

- This is a toy example so it's easy to tell where the problem is. How can you make your error more informative? 

# Solution 

## Try-catch 

- There are three kinds of messages you will run into, if your code has an error based on the following functions.  

    - stop(): errors; Functions must stop. 
    - warning(): warnings; Functions may still work. Nonetheless, something is possibly messed up. 
    - message(): messages; Some actions happened. 
    
- The basic logic of `try-catch`, R's basic error handling function, works like the following. 

```{r}

tryCatch(
  {map(url_lists, read_html) 
    }, warning = function(w) {
                "Warning"
    }, error = function(e) {
                "Error"
    }, finally = {
                "Message"
})

```

- Here's `purrr` version of the `try-catch` mechanism (evaluates code and assigns exception handlers). 

## safely and possibly 

**Outputs** 

- result: result or `NULL`
- error: `NULL` or `error` 

```{r}

test <- map(url_lists, safely(read_html)) 

```

- The easier way to solve this problem is just avoiding the error.

```{r}

map(url_lists, safely(read_html)) %>%
  map("result") %>% # = map(function(x) x[["result"]]) = map(~.x[["name"]])
  purrr::compact() # Remove empty elements 

```

## possibly 

What if the best way to solve the problem is not ignoring the error ... 

```{r}

# If error occurred, "The URL is broken." will be stored in that element(s).
out <- map(url_lists, 
    
    possibly(read_html,
             otherwise = "The URL is broken.")
    
    ) 

out

# Let's find the broken URL.
url_lists[out[seq(out)] == "The URL is broken."]

```


